Modeling the Java Card API (or Interface?) in B

### 2012-03-29 trunk/papers/B2012-work/javacardAPIpaper.tex
codigos atualizados

\lstset{language=B, caption={B machine Buscard},label=lis:buscard}
\begin{lstlisting}
MACHINE
	Buscard
CONSTANTS
	maximum
PROPERTIES
	maximum : INTEGER & maximum = 100
VARIABLES
	balance
INVARIANT
	balance : INTEGER & balance <= maximum
INITIALISATION
	balance := 0
OPERATIONS
	add(credit) =
	PRE
		credit : INTEGER & credit > 0  & balance + credit <= maximum
	THEN
		balance := balance + credit
	END
END
\end{lstlisting}

@@

\lstset{language=Java, caption={Method add in applet Java Card},label=lis:addjavacard}
\begin{lstlisting}
public void add(APDU apdu) {
	byte[] buffer = apdu.getBuffer();
	byte credit = (byte) Util.makeShort((byte) buffer[ISO7816.OFFSET_P1], (byte)buffer[ISO7816.OFFSET_P2]);
	if (!(credit >= 0)) {
		ISOException.throwIt(EXCEPTIONS.negative_credit);
	}
	else if (!(balance + credit <= MAXIMUM)) {
		ISOException.throwIt(EXCEPTIONS.balance_exceeded);
	}
	else {
		balance = (balance + credit);
	}
}
\end{lstlisting}

\lstset{language=B, caption={B implementation},label=lis:addimplementation}
\begin{lstlisting}
add (apdu) =
	VAR 
		bf, cr,  apdu_state, res, curr_bal
	IN
		bf          <-- apdu.getBuffer;
		apdu_state  <-- apdu.getCurrentState;
		curr_bal <-- bal.get_num;

		IF (apdu_state = STATE_INITIAL) 
		THEN
			res <-- apdu.setIncomingAndReceive
		ELSIF (OFFSET_CDATA >= 0 &
			sum_short(OFFSET_CDATA, 2) <= size(bf) & 
			bf /= [])
		THEN 
			cr  <-- util.getShort(bf, OFFSET_CDATA);

			IF sum_short (curr_bal, cr) <= MAX_BALANCE & 
				sum_short (curr_bal, cr) >= 0 
			THEN 
				bal.add (cr)
			END
		END
END;
\end{lstlisting}

>>>>

\lstset{language=B, caption={B machine Buscard},label=lis:buscard}
\begin{lstlisting}
MACHINE
	Buscard
CONSTANTS
	maximum
PROPERTIES
	maximum : INTEGER & MAX_BALANCE  = 100
VARIABLES
	balance
INVARIANT
	balance : INTEGER & balance <= MAX_BALANCE 
INITIALISATION
	balance := 0
OPERATIONS
	add(credit) =
	PRE
		credit : INTEGER & credit > 0  & balance + credit <= MAX_BALANCE 
	THEN
		balance := balance + credit
	END
END
\end{lstlisting}

@@

\lstset{language=Java, caption={Method add in applet Java Card},label=lis:addjavacard}
\begin{lstlisting}
public void add (APDU apdu) { 
	byte[] bf;  short cr; byte apdu_state; short res;

	bf = apdu.getBuffer();
	apdu_state = apdu.getCurrentState();

	if (apdu_state == STATE_INITIAL) {
		res = apdu.setIncomingAndReceive();
	} else if (ISO7816.OFFSET_CDATA >= 0 && 
			(short) (ISO7816.OFFSET_CDATA + 2) <= bf.length && 
			bf != null) {

		cr = Util.getShort (bf, ISO7816.OFFSET_CDATA);

		if (!((short) (balance + cr) <= MAX_BALANCE)) {
			ISOException.throwIt(EX_BALANCE_EXCEEDED);
		} else if (!((short) (balance + cr) >= 0)) {
			ISOException.throwIt(EX_NEGATIVE_BALANCE);
		} else if (! (cr > 0)) {
			ISOException.throwIt(EX_NEGATIVE_CREDIT);
		} else {
			balance = (short) (balance + cr);
		}
	} 
}
\end{lstlisting}

\lstset{language=B, caption={B implementation},label=lis:addimplementation}
\begin{lstlisting}
add (apdu) = 
VAR 
	bf, cr, apdu_state, res
IN
	bf  <-- apdu.getBuffer;		
    	apdu_state  <-- apdu.getCurrentState;

	IF (apdu_state = STATE_INITIAL) 
	THEN
		res <-- apdu.setIncomingAndReceive                
	ELSIF (OFFSET_CDATA >= 0 &
		sum_short(OFFSET_CDATA, 2) <= size(bf) & 
		bf /= [])
	THEN 
		cr  <-- Util.getShort(bf, OFFSET_CDATA);

		IF not (sum_short (balance, cr) <= MAX_BALANCE)
		THEN 
			ISOException.throwIt(EX_BALANCE_EXCEEDED)
		ELSIF not (sum_short (balance, cr) >= 0)
		THEN ISOException.throwIt(EX_NEGATIVE_BALANCE)
		ELSIF not (cr > 0)
		THEN ISOException.throwIt(EX_NEGATIVE_CREDIT) 
		ELSE  
			balance := sum_short(balance, cr)
		END
	END
END
\end{lstlisting}
